Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Research question: include a paragrah about how the RQ fits into the bigger picture

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OpenStreetMap (OSM) data.
A key issue in creating 3D representations of geodata is that since individual features will be extruded to give them width, situations may arise where the generated 3D meshes are intersecting.

>>>>

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OpenStreetMap (OSM) data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (find reference)
